---
title: "Untitled"
author: "Mine Cetinkaya-Rundel"
date: "July 16, 2016"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(babynames)
library(stringr)
library(dplyr)
```


```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("initial", label = "Initial:",
              choices = letters, selected = "a", multiple = TRUE),
  
  selectInput("yes", label = "Letters wanted:",
              choices = letters, selected = "a", multiple = TRUE),
  
  selectInput("no", label = "Letters not wanted:",
              choices = letters, selected = "z", multiple = TRUE)
)

renderPlot({
  df <- 
  
  ggplot(data = babynames, aes(x = year, y = prop)) +
    geom_lines()
  
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



